Git Learning Notes

### 2015-01-15 ch-moox/moox.tex
all chapter fine tuned

Researchers have been exploring a variety of methods to synthesized different \ce{MoO3} nanostructures. Only a brief introduction will be given here, since these efforts has been well documented in several review articles.\cite{He2003} Most of these methods can be categorized into two groups: solution-based hydrothermal procedures \citep{Li2002b,Xia2006,Li2006a,Camacho-Bragado2006} and chemical vapor transport and deposition approaches.\citep{Zeng1998,Li2002c,Li2002d,Zhou2003b,Fibers2007,Yan2009}. Both methods have its own merits. Hydrothermal process usually need lower temperature(\textless 300 \si{\degreeCelsius}), but the duration is usually long and requires several post-growth processing steps; whereas vapor deposition demands relatively high temperature (\textgreater 500 \si{\degreeCelsius}) yet with a shorter time. Both methods are scalable for industrial applications. However the hydrothermal treatment seems to allow more  nanostructures control than does the vapor deposition method. Nanobelts,\cite{Li2002b} helical nanosheets, nanoflowers, prims-like rods\cite{Li2006a} and nanoribbons\cite{Camacho-Bragado2006} were obtained by the former one while nanoflakes,\cite{Chen2009} nanobelts\cite{Hu2009} and nanowires\citep{Zhou2003b,Chen2011b} dominated the product morphology for the latter one. The assistance of Au catalyst in vapor deposition only altered the orientation\cite{Yan2009} or served as preferred nucleation sites\cite{Cai2011} without producing new \ce{MoO3} structures. \citeauthor{Chithambararaj2013} prepared hexagonal \ce{MoO3} nanocrystal via hydrothermal method and demonstrated the photodegradation of methylene blue (MB) under visible light.\cite{Chithambararaj2013} The efficiency dependence on catalysis/dye ratio, light intensity and temperature was studied. h-\ce{MoO3} was mostly synthesized using solution methods, where \ce{NH4+} and \ce{OH-} were possible structure directing and stable agents. The band gap of h-\ce{MoO3} estimated from diffusion reflection spectrum is $2.8\sim3.0$ eV. Hexagonal phase of \ce{MoO3} is readily identified by the XRD pattern (strong peak at $2\theta=20^{\circ}$). It is worth noting that in spite of these numerous growth of \ce{MoO3}, reports on catalytic growth are still scarce.

@@

Silicon substrates was first cleaned according to the procedure in Sec.~\ref{ch2sub} on page~\pageref{ch2sub}. To apply the catalysts, 54 $\mu$L 10 mM \ce{NaOH} (or \ce{KI}, \ce{Na2CO3}) was drop-cast onto clean substrates and then naturally left dry in a convection hood. Other alkali ions-containing substrates, such as glass (Fisher Scientific, microscope slide, 12-549) and indium tin oxide (ITO) coated glass (Delta Technologies, 25\si{\ohm}), were cleaned by the same routine except the absence of plasma cleaning and subsequent aqueous solution dipping. Mica was cleaved right before growth without other treatment.

In a typical synthesis run (Fig.~\ref{fig:mooxgrowth}), about 2 g molybdenum powders were loaded into the uniform heating zone and the sealed chamber was first pumped down to 10 mTorr. Then oxygen flow varying between 0.1 sccm to 10 sccm (standard cubic centimeter per minute) was admitted from upstream inlet. With 10 sccm UHP Ar as carrier gas, the overall pressure reached about 200 mTorr. The heating temperature was ramped up to 800 \si{\degreeCelsius} in 30 min and lasted for 15 to 120 min. Then the heating power was turned off and the chamber was allowed to naturally cool down to room temperature. The substrate was placed in downstream location where the temperature was about 350 to 650 \si{\degreeCelsius} according to open air temperature profile. Non-catalytic growth shares the same procedure except the NaOH treatment.

@@

Based on this phase diagram and the growth conditions adopted in this study, it is predicted that the overall reactions occur in the following sequences. First, Mo powder is oxidized and \ce{MoO3} vapor is produced and transported to downstream by Ar carrier gas. Then NaOH reacts with incoming \ce{MoO3} according to Formula~\ref{eq:pd}. 
\begin{subequations}\label{eq:pd}
\begin{align}
\cee{NaOH(l) + MoO3(g) &\rightarrow Na2MoO4(l) + H2O(g)\\
Na2MoO4 + nMoO3   &\rightarrow Na2O.(n + 1)MoO3}
\end{align}
\end{subequations}
The melting point of \ce{Na2MoO4} is 687 \si{\degreeCelsius}. Based on the open air temperature profile (Fig.~\ref{fig:mooxgrowth}), the substrate is located in temperature zone between 650 and 350 \si{\degreeCelsius}. The actual temperature distribution during growth is different from ambient measurement due to the pressure change and thermal conduction along the Si substrate. It is difficult to acquire the accurate values along the substrate; however, by considering the flow rate, the actual temperature will be higher than predicted by open air measurement.\cite{Subannajui2010} The melting of \ce{Na2MoO4} is highly possible when taking into account of its size as well.\cite{Bruggemann1997} The continuous supply of \ce{MoO3} growth species will push the phase evolution towards high \ce{MoO3} molar ratio end, with $n$ in \ce{Na2O.nMoO3} increasing from 1 to 4. Each site of \ce{Na2MoO4} will continue absorb incoming \ce{MoO3}, forming a swelling droplet. \ce{MoO3} will precipitate from these seeds when a critical supersaturation concentration is reached, which is about 75\% in unit of mole according to Fig.~\ref{fig:ch4pd}.\footnote{This ratio considerably exceeds that of the usual metal catalyst scenario. This high solubility accounts for several observations in current experiments: the dimensions of individual deposit is much larger than that of initial droplet, the concentration of sodium in final products is extremely low.}    Based on this aforementioned analysis, the author propose a hypothesis:
%theorem environment

@@

Fig.~\ref{fig:ch4al2}a-c illustrate the forked plate growth on \ce{Na2CO3} treated Si, sword-shape belts on glass, and nanoblets growth on mica, respectively. No long belt or tower was observed on the sample with \ce{Na2CO3}. Long belts found on mica (\ce{K(Al2)(Si3Al)O10(OH)2}) probably arise from potassium-catalyzed \gls{vls} mechanism.\cite{Hu2011} More detailed results on glass will be presented in Sec.~\ref{sec:glass}.

@@

This thesis studied the effect of temperature, oxygen partial pressure and growth time towards \ce{MoO3} deposition on glass substrates. Each factor was divided into two levels, with $T$ at 700 and 800 \si{\degreeCelsius}, \ce{O2} flow at 1 and 10 sccm, and growth time of 15 and 60 min. And the morphological variations revealed by SEM imaging were summarized in Table~\ref{tab:mo3glass}.
% glass growth matrix
\begin{table}[htb]
\centering
\caption{\ce{MoO3} growth on glass}\label{tab:mo3glass}
\begin{tabular}{lccp{3in}}
\toprule
\multicolumn{3}{c}{Growth Conditions} \\
\cmidrule(l){1-3}
$T$ (\si{\degreeCelsius}) & \ce{O2} (sccm) & Time (min) & Morphology  \\
\midrule
700    &  10   & 15  &   about 50 $\mu$m belts, some towers \\
700   &  1   & 60  &   irregular shape, not too much growth\\
700    &  10   & 60  &   droplet almost all on tip of belts, many towers \\
800    &  1   & 15  &   tens $\mu$m belt with sharp edge(100 nm thick, and 1micro wide) dominates\\
800   &  1   & 60  &   exhibiting ITO features, droplets on tips of belt, many tower like structures\\
800    &  10   & 15  &   rounded edge flakes dominate, modest density tapering belt, and some possible tower\\
800    &  10   & 60  &   ITO/glass features, aggregated belts, some towers\\
\bottomrule
\end{tabular}
\end{table}
The 800-1-15 combination produced dense \ce{MoO3} nanoplate with length about 10 $\mu$m, width $300\sim500$ nm and thickness less than 100 nm, as illustrated in Fig.~\ref{fig:ch4glass}. These \ce{MoO3} nanoplates are of high crystalline quality, and could potentially show enhanced photoelectrochemical and electrochromic activities. 
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{moo3_glass}
\caption[Optimized \ce{MoO3} nanoplates growth on glass]{Optimized \ce{MoO3} nanoplates growth on glass.}
\label{fig:ch4glass}
\end{figure}

>>>>

Researchers have been exploring a variety of methods to synthesized different \ce{MoO3} nanostructures. Only a brief introduction will be given here, since these efforts has been well documented in several review articles.\cite{He2003} Most of these methods can be categorized into two groups: solution-based hydrothermal procedures \citep{Li2002b,Xia2006,Li2006a,Camacho-Bragado2006} and chemical vapor transport and deposition approaches.\citep{Zeng1998,Li2002c,Li2002d,Zhou2003b,Fibers2007,Yan2009} Both methods have its own merits. Hydrothermal process usually need lower temperature(\textless 300 \si{\degreeCelsius}), but the duration is usually long and requires several post-growth processing steps; whereas vapor deposition demands relatively high temperature (\textgreater 500 \si{\degreeCelsius}) yet with a shorter time. Both methods are scalable for industrial applications. However the hydrothermal treatment seems to allow more  nanostructures control than does the vapor deposition method. Nanobelts,\cite{Li2002b} helical nanosheets, nanoflowers, prims-like rods\cite{Li2006a} and nanoribbons\cite{Camacho-Bragado2006} were obtained by the former one while nanoflakes,\cite{Chen2009} nanobelts\cite{Hu2009} and nanowires\citep{Zhou2003b,Chen2011b} dominated the product morphology for the latter one. The assistance of Au catalyst in vapor deposition only altered the orientation\cite{Yan2009} or served as preferred nucleation sites\cite{Cai2011} without producing new \ce{MoO3} structures. \citeauthor{Chithambararaj2013} prepared hexagonal \ce{MoO3} nanocrystal via hydrothermal method and demonstrated the photodegradation of methylene blue (MB) under visible light.\cite{Chithambararaj2013} The efficiency dependence on catalysis/dye ratio, light intensity and temperature was studied. h-\ce{MoO3} was mostly synthesized using solution methods, where \ce{NH4+} and \ce{OH-} were possible structure directing and stable agents. The band gap of h-\ce{MoO3} estimated from diffusion reflection spectrum is $2.8\sim3.0$ eV. Hexagonal phase of \ce{MoO3} is readily identified by the XRD pattern (strong peak at $2\theta=20^{\circ}$). It is worth noting that in spite of these numerous growth of \ce{MoO3}, reports on catalytic growth are still scarce.

@@

Silicon substrates was first cleaned according to the procedure in Sec.~\ref{ch2sub} on page~\pageref{ch2sub}. To apply the catalysts, 54 $\mu$L 10 mM \ce{NaOH} (or \ce{KI}, \ce{Na2CO3}) was drop-cast onto clean substrates and then naturally left dry in a convection hood. Other alkali ions-containing substrates, such as glass (Fisher Scientific, microscope slide, 12-549) and indium tin oxide (ITO) coated glass (Delta Technologies, 25\si{\ohm}), were cleaned by the same routine except the absence of plasma cleaning and subsequent aqueous solution dipping. Mica was cleaved right before growth without other treatment. 
\begin{table}[htb]
\centering
\caption{Physical constants of reactants }\label{tb:mothermo}
\begin{tabular}{lccr}
\toprule
Material & MP(\si{\degreeCelsius}) & BP(\si{\degreeCelsius}) & Reference\\
\midrule
\ce{NaOH}        & 318 & 1388 & \cite{crc1977}  \\
\ce{NaI}        & 651 & 1300 & \cite{crc1977}    \\
\ce{KI}        & 681 & 1330 & \cite{crc1977}   \\
\ce{Na2CO3}        & 851 & Not determined & \cite{crc1977}    \\
\ce{Na2MoO4}        & 687 & Not available & \cite{crc1977}   \\
\ce{MoO3}    & 795 & 1155 & \cite{crc1977}   \\
\ce{MoO2}    & 1100(decomp) & Not available & MSDS   \\
\bottomrule
\end{tabular}
\end{table}
In a typical synthesis run (Fig.~\ref{fig:mooxgrowth}), about 2 g molybdenum powders were loaded into the uniform heating zone and the sealed chamber was first pumped down to 10 mTorr. Then oxygen flow varying between 0.1 sccm to 10 sccm (standard cubic centimeter per minute) was admitted from upstream inlet. With 10 sccm UHP Ar as carrier gas, the overall pressure reached about 200 mTorr. The heating temperature was ramped up to 800 \si{\degreeCelsius} in 30 min and lasted for 15 to 120 min. Then the heating power was turned off and the chamber was allowed to naturally cool down to room temperature. The substrate was placed in downstream location where the temperature was about 350 to 650 \si{\degreeCelsius} according to open air temperature profile. Non-catalytic growth shares the same procedure except the NaOH treatment.

@@

Based on this phase diagram, the physical constants of reactants in Table~\ref{tb:mothermo}, and the growth conditions adopted in this study, it is predicted that the overall reactions occur in the following sequences. First, Mo powder is oxidized and \ce{MoO3} vapor is produced and transported to downstream by Ar carrier gas. Then NaOH reacts with incoming \ce{MoO3} according to Formula~\ref{eq:pd}. 
\begin{subequations}\label{eq:pd}
\begin{align}
\cee{NaOH(l) + MoO3(g) &\rightarrow Na2MoO4 + H2O(g)\\
Na2MoO4 + nMoO3   &\rightarrow Na2O.(n + 1)MoO3}
\end{align}
\end{subequations}
The melting point of \ce{Na2MoO4} is 687 \si{\degreeCelsius}. Based on the open air temperature profile (Fig.~\ref{fig:mooxgrowth}), the substrate is located in temperature zone between 650 and 350 \si{\degreeCelsius}. The actual temperature distribution during growth is different from ambient measurement due to the pressure change and thermal conduction along the Si substrate. It is difficult to acquire the accurate values along the substrate; however, by considering the flow rate, the actual temperature will be higher than predicted by open air measurement.\cite{Subannajui2010} The melting of \ce{Na2MoO4} is highly possible when taking into account of its size as well.\cite{Bruggemann1997} The continuous supply of \ce{MoO3} growth species will push the phase evolution towards high \ce{MoO3} molar ratio end, with $n$ in \ce{Na2O.nMoO3} increasing from 1 to 4. Each site of \ce{Na2MoO4} will continue absorb incoming \ce{MoO3}, forming a swelling droplet. \ce{MoO3} will precipitate from these seeds when a critical supersaturation concentration is reached, which is about 75\% in unit of mole according to Fig.~\ref{fig:ch4pd}.\footnote{This ratio considerably exceeds that of the usual metal catalyst scenario. This high solubility accounts for several observations in current experiments: the dimensions of individual deposit is much larger than that of initial droplet, the concentration of sodium in final products is extremely low.}    Based on this aforementioned analysis, the author propose a hypothesis:
%theorem environment

@@

Fig.~\ref{fig:ch4al2}a-c illustrate the forked plate growth on \ce{Na2CO3} treated Si, sword-shape belts on glass, and nanoblets growth on mica, respectively. No long belt or tower was observed on the sample with \ce{Na2CO3}. Long belts found on mica (\ce{K(Al2)(Si3Al)O10(OH)2}) probably arise from potassium-catalyzed \gls{vls} mechanism.\cite{Hu2011}

@@

This thesis studied the effect of temperature, oxygen partial pressure and growth time towards \ce{MoO3} deposition on glass substrates. Each factor was divided into two levels, with $T$ at 700 and 800 \si{\degreeCelsius}, \ce{O2} flow at 1 and 10 sccm, and growth time of 15 and 60 min. And the morphological variations revealed by SEM imaging were summarized in Table~\ref{tab:mo3glass}.
% glass growth matrix
\begin{table}[htb]
\centering
\caption{\ce{MoO3} growth on glass}\label{tab:mo3glass}
\begin{tabular}{lccp{3in}}
\toprule
\multicolumn{3}{c}{Growth Conditions} \\
\cmidrule(l){1-3}
$T$ (\si{\degreeCelsius}) & \ce{O2} (sccm) & Time (min) & Morphology  \\
\midrule
700    &  10   & 15  &   about 50 $\mu$m belts, some towers \\
700   &  1   & 60  &   irregular shape, not too much growth\\
700    &  10   & 60  &   droplet almost all on tip of belts, many towers \\
800    &  1   & 15  &   tens $\mu$m belt with sharp edge(100 nm thick, and 1micro wide) dominates\\
800   &  1   & 60  &   exhibiting ITO features, droplets on tips of belt, many tower like structures\\
800    &  10   & 15  &   rounded edge flakes dominate, modest density tapering belt, and some possible tower\\
800    &  10   & 60  &   ITO/glass features, aggregated belts, some towers\\
\bottomrule
\end{tabular}
\end{table}
The 800-1-15 combination produced dense \ce{MoO3} nanoplate with length about 10 $\mu$m, width $300\sim500$ nm and thickness less than 100 nm, as illustrated in Fig.~\ref{fig:ch4glass}. These \ce{MoO3} nanoplates are of high crystalline quality, and could potentially show enhanced photoelectrochemical and electrochromic activities. 
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{moo3_glass_lbd}
\caption[Optimized \ce{MoO3} nanoplates growth on glass]{Optimized \ce{MoO3} nanoplates growth on glass.}
\label{fig:ch4glass}
\end{figure}
